### 2024-10-16 basic-statistics.qmd
20241016 - reorder figure labels

```{r}
#| layout-ncol: 2
#| fig-cap: "Interpretation of *p*-Values When Examining The Differences Between Groups. The vertical black lines reflect the group means."
#| fig-alt: "Interpretation of *p*-Values When Examining The Differences Between Groups. The vertical black lines reflect the group means."
#| fig-subcap: 
#|   - "What is the probability my data would look like this..."
#|   - "...if in the population, the groups were really this?"
#| label: fig-pValuesDifference
#| code-fold: true

@@

```{r}
#| layout-ncol: 2
#| fig-cap: "Interpretation of *p*-Values When Examining The Association Between Variables."
#| fig-alt: "Interpretation of *p*-Values When Examining The Association Between Variables."
#| fig-subcap: 
#|   - "What is the probability my data would look like this..."
#|   - "...if in the population, the association was really this?"
#| label: fig-pValuesAssociation
#| code-fold: true

>>>>

```{r}
#| label: fig-pValuesDifference
#| layout-ncol: 2
#| fig-cap: "Interpretation of *p*-Values When Examining The Differences Between Groups. The vertical black lines reflect the group means."
#| fig-alt: "Interpretation of *p*-Values When Examining The Differences Between Groups. The vertical black lines reflect the group means."
#| fig-subcap: 
#|   - "What is the probability my data would look like this..."
#|   - "...if in the population, the groups were really this?"
#| code-fold: true

@@

```{r}
#| label: fig-pValuesAssociation
#| layout-ncol: 2
#| fig-cap: "Interpretation of *p*-Values When Examining The Association Between Variables."
#| fig-alt: "Interpretation of *p*-Values When Examining The Association Between Variables."
#| fig-subcap: 
#|   - "What is the probability my data would look like this..."
#|   - "...if in the population, the association was really this?"
#| code-fold: true

### 2024-10-16 cognitive-bias.qmd
20241016 - reorder figure labels

```{r}
#| fig-cap: "Histogram of Number of Coins that Flip Heads-Up in a Simulation of 10 Coin Flips (with 100,000 Replications)."
#| fig-alt: "Histogram of Number of Coins that Flip Heads-Up in a Simulation of 10 Coin Flips (with 100,000 Replications)."
#| label: fig-simulationOf10CoinFlips
#| code-fold: true

>>>>

```{r}
#| label: fig-simulationOf10CoinFlips
#| fig-cap: "Histogram of Number of Coins that Flip Heads-Up in a Simulation of 10 Coin Flips (with 100,000 Replications)."
#| fig-alt: "Histogram of Number of Coins that Flip Heads-Up in a Simulation of 10 Coin Flips (with 100,000 Replications)."
#| code-fold: true

### 2024-10-16 evaluating-prediction-accuracy.qmd
20241016 - reorder figure labels

```{r}
#| fig-cap: "Distribution of Test Scores by Berry Type."
#| fig-alt: "Distribution of Test Scores by Berry Type."
#| label: fig-classificationDistributions
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on a Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on a Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationStandardCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on Raising the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on Raising the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationRaiseCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Classifications Based on Lowering the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on Lowering the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| label: fig-classificationLowerCutoff
#| code-fold: true

@@

```{r}
#| fig-cap: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| fig-alt: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| label: fig-aucRange
#| fig-width: 8
#| fig-height: 8
#| code-fold: true

>>>>

```{r}
#| label: fig-classificationDistributions
#| fig-cap: "Distribution of Test Scores by Berry Type."
#| fig-alt: "Distribution of Test Scores by Berry Type."
#| code-fold: true

@@

```{r}
#| label: fig-classificationStandardCutoff
#| fig-cap: "Classifications Based on a Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on a Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| code-fold: true

@@

```{r}
#| label: fig-classificationRaiseCutoff
#| fig-cap: "Classifications Based on Raising the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on Raising the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| code-fold: true

@@

```{r}
#| label: fig-classificationLowerCutoff
#| fig-cap: "Classifications Based on Lowering the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| fig-alt: "Classifications Based on Lowering the Cutoff. Note that some true negatives and true positives are hidden behind the false positives and false negatives."
#| code-fold: true

@@

```{r}
#| label: fig-aucRange
#| fig-cap: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| fig-alt: "Receiver Operating Characteristic (ROC) Curves for Various Levels of Area Under The ROC Curve (AUC) for Various Measures."
#| fig-width: 8
#| fig-height: 8
#| code-fold: true
